---
title: "Pipes and ggplot Exercises"
author: "Jennifer Lin"
date: "4/14/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set Up

```{r}
# *********************************************************************
# PACKAGES AND FUNCTIONS ###########
# *********************************************************************

library(dplyr)
library(readr)
library(ggplot2)

# *********************************************************************
# DATA ###########
# *********************************************************************

# Load Data
CCES_2018 <- read_csv(here::here("CCES18_subset.csv"))

```


# `dplyr` Exercises

## Exercise `

We are interested in approval to a political institution. Think about the institution you want to focus on (and a second) and do the following:


1. Select the state, region, party, and two approval variables of choice (Congress, President, Supreme Court)

2. Filter out the NA values on state and party variables. Hint: use `is.na()` and `!`.

```{r}

```

## Exercise 2

In the data frame that you previously created that took out region, state, party, and approval variables, create a summary table that describes the precent of people in each state-party-region combination that approves your institution of choice. Use mutate and `case_when()` to recode your region variable so that 1 = Northeast, 2 = Midwest, 3 = South and 4 = West.

HINT - You can put multiple variables in the `group_by()` command

HINT - To create a proportion variable, use can use the following function in the summarise environment. NOTE how the approval variables are coded (1 = approve, 2 = disapprove)

```{r, eval = FALSE}
sum(appVar == 1, na.rm = TRUE)/length(appVar)
```

```{r}

```

# `ggplot` Exercises

## Exercise 1

Using the data frame that you created (or `state_party_Congress`), create a very basic graph like the demos above. Take some time to play around with the possible graphs in ggplot. The goal is to get you to feel comfortable with the data and the plot layers.

```{r}

```

## Exercise 2

Using the plot that you created in the previous exercise, do the following

1. Add a title, x and y axis labels
2. Edit the legend to fit your graph
3. Change the theme

```{r}

```

# Spatial Data Exercises

The CCES has data for respondents from nearly every state.

```{r}
library(tigris)
library(sf)
```

Pick a state (not Illinois) and do the following:

1. Get the state's county shape files with `tigris`

```{r, results='hide'}
IL_county <- counties("IL", cb = TRUE)
```

```{r}

```


2. Adopt the following code to your state to find the number of people who respond to the CCES by county, identified with `countyfips`

```{r}
IL <- CCES_2018 %>% filter(state == "IL") %>% 
  group_by(countyfips) %>% 
  summarise(
    n = n(),
    .groups = 'keep'
  ) 
```

```{r}

```


## Exercise 2

Take the mapping code and adjust it to your data


```{r}
IL_respondents <- left_join(
  IL_county,
  IL,
  by = c("GEOID" = "countyfips")
) %>% 
  mutate(
    respondents = ifelse(is.na(n), 0, n)
  )
```

```{r}

```


```{r maps}
ggplot()+
  geom_sf(
    data = IL_respondents, 
    aes(fill = respondents))+
  scale_fill_gradient(
    low = "gray100",
    high = "gray0",
    na.value = "black", 
    limits   = c(0, 100)
  )+
  labs(
    title    = "Illinois",
    subtitle = "Number of CCES Respondents from Each County", 
    fill     = "Number of \n Respondents"
  )+
  theme_void()
```

```{r}

```


While you are at it, add a title and see what happens when you change the limits under `scale_fill_gradient()`

